An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-16 VLDB2026/main.tex
Update main.tex

To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an Out-of-Distribution (OOD) dataset to the three standard datasets and tested performance under large-range queries. As shown in Figure~\ref{fig:exp_8_3}, most methods performed worst on the Text2Image dataset. This is because OOD queries make the $k$-nearest neighbor distribution more sparse. As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.

>>>>

To evaluate the robustness of the RF-ANNS algorithm in different scenarios, we added an OOD dataset to the three standard datasets and tested performance under large-range queries. As shown in Figure~\ref{fig:exp_8_3}, most methods performed worst on the Text2Image dataset. This is because OOD queries make the $k$-nearest neighbor distribution more sparse. As a result, the search needs to visit more nodes, which leads to an exponential growth in the search space and a sharp drop in efficiency.
